%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
%
% Adapted to be an Rmarkdown template by Mitchell O'Hara-Wild
% 23 November 2018
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%
%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight

\definecolor{awesome}{HTML}{414141}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{true}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}

\def\endfirstpage{\newpage}

%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right

\name{Philip T.}{Leftwich}


\mobile{+44 7871 041 012}
\email{\href{mailto:p.leftwich@uea.ac.uk}{\nolinkurl{p.leftwich@uea.ac.uk}}}
\homepage{philip-leftwich.github.io}
\github{Philip-Leftwich}
\linkedin{philip-leftwich-117052155}
\twitter{philipleftwich}

% \gitlab{gitlab-id}
% \stackoverflow{SO-id}{SO-name}
% \skype{skype-id}
% \reddit{reddit-id}


\usepackage{booktabs}

\providecommand{\tightlist}{%
	\setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%------------------------------------------------------------------------------


\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[R]{\thepage}

% Pandoc CSL macros
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[3] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
% 2019-02-14 Chris Umphlett - add flexibility to the document name in footer, rather than have it be static Curriculum Vitae
\makecvfooter
  {April 14, 2021}
    {Philip T. Leftwich~~~·~~~Curriculum Vitae}
  {\thepage}


%-------------------------------------------------------------------------------
%	CV/RESUME CONTENT
%	Each section is imported separately, open each file in turn to modify content
%------------------------------------------------------------------------------



\hypertarget{education}{%
\section{Education}\label{education}}

\begin{cventries}
    \cventry{University of East Anglia}{PhD}{Norwich}{2009 - 2013}{\begin{cvitems}
\item Thesis: Male Reproductive Success and Population Control in the Mediterranean Fruit Fly.
\end{cvitems}}
    \cventry{Durham University}{BSc (Hons) / Zoology}{Durham}{2004 - 2008}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{qualifications}{%
\section{Qualifications}\label{qualifications}}

\begin{cventries}
    \cventry{Higher Education Academy}{HEA Fellow}{York}{2016}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{grants}{%
\section{Grants}\label{grants}}

\begin{cventries}
    \cventry{Gifts that keep on giving: maternal effects and insect pest control}{BBSRC}{University of East Anglia}{2020}{\begin{cvitems}
\item PhD studentship
\item Co-supervisor
\item Funding amount 100,000 GBP
\end{cvitems}}
    \cventry{CRISPR Cas9 based sex-conversion gene drives for pest insect management}{BBSRC}{University of East Anglia}{2019}{\begin{cvitems}
\item PhD studentship
\item Co-supervisor
\item Funding amount 100,000 GBP
\end{cvitems}}
    \cventry{Entomology Program Enhancement}{Entomological Society of America}{Pirbright Institute}{2018}{\begin{cvitems}
\item Travel
\item Funding amount 1000 GBP
\end{cvitems}}
    \cventry{Introduction to bioinformatics resources for vector genomics studies}{Infravec}{Pirbright Institute}{2018}{\begin{cvitems}
\item Training
\item Funding amount 460 GBP
\end{cvitems}}
    \cventry{Colonization, Domestication and Population control in pest insects}{BBSRC}{University of East Anglia}{2012}{\begin{cvitems}
\item Research grant
\item Researcher Co-I
\item Funding amount 376,000 GBP
\end{cvitems}}
\end{cventries}

\hypertarget{teaching}{%
\section{Teaching}\label{teaching}}

\begin{cventries}
    \cventry{Module Organiser}{Data Science for Biologists}{University of East Anglia}{2020-present}{}\vspace{-4.0mm}
    \cventry{Module Organiser}{Genetics}{University of East Anglia}{2019-present}{}\vspace{-4.0mm}
    \cventry{Lecturer}{Genes, Genomes and Genomics}{University of East Anglia}{2019-present}{}\vspace{-4.0mm}
    \cventry{Tutor}{Skills for Biologists}{University of East Anglia}{2019-present}{}\vspace{-4.0mm}
    \cventry{Guest Speaker}{Medical Entomology}{LSHTM}{2017-2018}{}\vspace{-4.0mm}
    \cventry{Lecturer}{Science Communication}{University of East Anglia}{2015-present}{}\vspace{-4.0mm}
    \cventry{Lecturer}{Microbiology}{University of East Anglia}{2015-present}{}\vspace{-4.0mm}
    \cventry{Fieldwork co-ordinator}{Field Ecology}{University of East Anglia}{2015-present}{}\vspace{-4.0mm}
    \cventry{Module Organiser}{Biodiversity}{University of East Anglia}{2015-2016}{}\vspace{-4.0mm}
    \cventry{Module Organiser}{Evolution, Behaviour and Ecology}{University of East Anglia}{2015-2016}{}\vspace{-4.0mm}
    \cventry{Tutor}{Evolution, Health and Disease}{University of East Anglia}{2013-2019}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{presentations}{%
\section{Presentations}\label{presentations}}

\hypertarget{conferences}{%
\subsection{Conferences}\label{conferences}}

\hypertarget{seminars}{%
\subsection{Seminars}\label{seminars}}

\hypertarget{outreach}{%
\subsection{Outreach}\label{outreach}}

\hypertarget{selected-media-coverage}{%
\subsection{Selected Media coverage}\label{selected-media-coverage}}

\hypertarget{administrative-duties}{%
\section{Administrative Duties}\label{administrative-duties}}

\begin{cventries}
    \cventry{School of Biological Sciences}{Chair of Extenuating Circumstances Panel}{University of East Anglia}{2021-present}{}\vspace{-4.0mm}
    \cventry{School of Biological Sciences}{Student Partnership Officer}{University of East Anglia}{2019-present}{}\vspace{-4.0mm}
\end{cventries}

\hypertarget{consultancy}{%
\section{Consultancy}\label{consultancy}}

\hypertarget{professional-service}{%
\section{Professional Service}\label{professional-service}}

\newpage

\hypertarget{publications}{%
\section{Publications}\label{publications}}

\textbf{h-index: 9}, \textbf{Number of Publications: 19},
\textbf{Citations: 308}

\hypertarget{refereed-journal-papers}{%
\subsection{Refereed Journal Papers}\label{refereed-journal-papers}}

\hypertarget{refs_journals}{}
\leavevmode\hypertarget{ref-13}{}%
\textbf{Leftwich,} P., Spurgin, L., Harvey-Samuel, T., Thomas, C.,
Paladino, L., Edgington, M., \& Alphey, L. (2021). Genetic pest
management and the background genetics of release strains.
\emph{Philosophical Transactions of the Royal Society B},
\emph{376}(1818).

\leavevmode\hypertarget{ref-11}{}%
Anderson, M., Purcell, J., Verkuijl, S., Norman, V., \textbf{Leftwich,}
P., Harvey-Samuel, T., \& Alphey, L. (2020). Expanding the CRISPR
toolbox in culicine mosquitoes: In vitro validation of pol III
promoters. \emph{ACS Synthetic Biology}, \emph{9}(3), 678--681.

\leavevmode\hypertarget{ref-14}{}%
\textbf{Leftwich,} P., Edgington, M., \& Chapman, T. (2020).
Transmission efficiency drives host--microbe associations.
\emph{Proceedings of the Royal Society B}, \emph{287}(1934).

\leavevmode\hypertarget{ref-16}{}%
Tng, P., Paladino, L., Verkuijl, S., Purcell, J., Merits, A.,
\textbf{Leftwich,} P., Fragkoudis, R., Noad, R., \& Alphey, L. (2020).
Cas13b-dependent and Cas13b-independent RNA knockdown of viral sequences
in mosquito cells following guide RNA expression. \emph{Communications
Biology}, \emph{3}(1), 1--9.

\leavevmode\hypertarget{ref-15}{}%
\textbf{Leftwich,} P., Nash, W., Friend, L., \& Chapman, T. (2019).
Contribution of maternal effects to dietary selection in mediterranean
fruit flies. \emph{Evolution}, \emph{73}(2), 278--292.

\leavevmode\hypertarget{ref-6}{}%
Redford, K., Brooks, T., Macfarlane, N., Adams, J., Alphey, L., Bennet,
E., Delborne, J., Eggermont, H., Esvelt, K., Kingirl, A., Kokotovich,
A., Kolodziejczyk, B., Kuiken, T., Mead, A., Oliva, M., Perello, E.,
Slobodian, L., Thizy, D., Tompkins, D., Winter, G., Campbell, K.,
Elsensohn, J., Holmes, N., Farmer, C., Keitt, B., \textbf{Leftwich,} P.,
Maloney, T., Masiga, D., Newhouse, A., Novak, B., \ldots{} Oppen, M.
(2019). \emph{Genetic frontiers for conservation: An assessment of
synthetic biology and biodiversity conservation}.

\leavevmode\hypertarget{ref-17}{}%
\textbf{Leftwich,} P., \& Chapman, T. (2018). Testing for assortative
mating by diet in drosophila melanogaster. \emph{Bio-Protocol},
\emph{8}(20).

\leavevmode\hypertarget{ref-3}{}%
\textbf{Leftwich,} P., Clarke, N., Hutchings, M., \& Chapman, T. (2018).
Gut microbiomes and reproductive isolation in drosophila (vol 114, pg
12767, 2017). \emph{Proceedings of the National Academy of Sciences},
\emph{115}(10).

\leavevmode\hypertarget{ref-10}{}%
\textbf{Leftwich,} P., Clarke, N., Hutchings, M., \& Chapman, T. (2018).
Reply to obadia et al.: Effect of methyl paraben on host--microbiota
interactions in drosophila melanogaster. \emph{Proceedings of the
National Academy of Sciences}, \emph{201805499}.

\leavevmode\hypertarget{ref-5}{}%
\textbf{Leftwich,} P., Edgington, M., Harvey-Samuel, T., Paladino, L.,
Norman, V., \& Alphey, L. (2018). Recent advances in threshold-dependent
gene drives for mosquitoes. \emph{Biochemical Society Transactions},
\emph{46}(5), 1203--1212.

\leavevmode\hypertarget{ref-12}{}%
\textbf{Leftwich,} P., Hutchings, M., \& Chapman, T. (2018). Diet, gut
microbes and host mate choice: Understanding the significance of
microbiome effects on host mate choice requires a case by case
evaluation. \emph{Bioessays}, \emph{40}(12).

\leavevmode\hypertarget{ref-8}{}%
\textbf{Leftwich,} PT., Clarke, NV. E., Hutchings, MI., \& Chapman, T.
(2018). Reply to rosenberg et al.: Diet, gut bacteria, and assortative
mating in drosophila melanogaster. \emph{Proceedings of the National
Academy of Sciences, Https://Doi.org/}, \emph{10}.

\leavevmode\hypertarget{ref-9}{}%
\textbf{Leftwich,} P., Nash, W., Friend, L., \& Chapman, T. (2017).
Adaptation to divergent larval diets in the medfly, ceratitis capitata.
\emph{Evolution}, \emph{71}(2), 289--303.

\leavevmode\hypertarget{ref-7}{}%
Longdon, B., Day, J., Schulz, N., \textbf{Leftwich,} P., Jong, Ma.,
Breuker, C., Gibbs, M., Obbard, D., Wilfert, L., Smith, S., McGonigle,
J., Houslay, T., Wright, L., Livraghi, L., Evans, L., Friend, L.,
Chapman, T., Vontas, J., Kambouraki, N., \& Jiggins, F. (2017).
Vertically transmitted rhabdoviruses are found across three insect
families and have dynamic interactions with their hosts.
\emph{Proceedings of the Royal Society B: Biological Sciences},
\emph{284}(1847).

\leavevmode\hypertarget{ref-1}{}%
\textbf{Leftwich,} P., Bolton, M., \& Chapman, T. (2016). Evolutionary
biology and genetic techniques for insect control. \emph{Evolutionary
Applications}, \emph{9}(1), 212--230.

\leavevmode\hypertarget{ref-2}{}%
\textbf{Leftwich,} P., Koukidou, M., Rempoulakis, P., Gong, H.-F.,
Zacharopoulou, A., Fu, G., Chapman, T., Economopoulos, A., Vontas, J.,
\& Alphey, L. (2014). Genetic elimination of field-cage populations of
mediterranean fruit flies. \emph{Proceedings of the Royal Society B:
Biological Sciences}, \emph{281}(1792).

\leavevmode\hypertarget{ref-18}{}%
Alphey, L., Ant, T., Koukidou, M., \textbf{Leftwich,} P., Rempoulakis,
P., Vontas, J., Economopoulos, A., \& Chapman, T. (2012). Genetic
improvements to sterile-male control of tephritid fruit flies.
\emph{Tephritid Workers of Europe and Middle East (TEAM),
Https://Nucleus.iaea.org~\ldots, 201}, \emph{2}.

\leavevmode\hypertarget{ref-4}{}%
\textbf{Leftwich,} P., Edward, D., Alphey, L., Gage, M., \& Chapman, T.
(2012). Variation in adult sex ratio alters the association between
courtship, mating frequency and paternity in the lek-forming fruitfly
ceratitis capitata. \emph{Journal of Evolutionary Biology},
\emph{25}(9), 1732--1740.

\hypertarget{working-papers-under-revision-or-review}{%
\subsection{Working Papers under Revision or
Review}\label{working-papers-under-revision-or-review}}

\hypertarget{refs_working_paper}{}
\leavevmode\hypertarget{ref-1}{}%
Harvey-Samuel, T., Xu, X., Lovett, E., Dafa'alla, T., Walker, A.,
Norman, V., Carter, R., Teal, J., Akilan, L., \textbf{Leftwich,} P., \&
Alphey, L. (2020). Engineered expression of the invertebrate-specific
scorpion toxin AaHIT reduces adult longevity and female fecundity in the
diamondback moth plutella xylostella. \emph{bioRxiv}.

\hypertarget{books}{%
\subsection{Books}\label{books}}

\hypertarget{refs_proceedings}{}
\leavevmode\hypertarget{ref-1}{}%
Penny, J., \& \textbf{Leftwich,} P. (2018). \emph{Maths skills for
a-level biology} {[}Technical report{]}. OUP (Oxford).

\end{document}
